Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-03-15 draft.tex
Updates from Overleaf

To correct for these incompleteness, we follow a similar method to that used in the Palomar Transient Factory rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}. We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}. We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA}; \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}. We simulate $1.1\times 10^6$ SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$. The SNe are generated and trained in the same way as for the training of SNN. SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}. The SNe are simulated with explosion epochs $t_0$ uniformly distributed between two months before DES-SN began and two months after it finished in order to account for all SNe that could have been observed by DES-SN. We run mock versions of the DES-SN survey, using the exact cadence, conditions, and zeropoints from the survey itself. All of the detected simulated SNe are passed through the light curve fit of SALT2 \citep{Betoule2014}, as per the implementation in \texttt{SNANA}, and those that fail the light curve cuts outlined in Section \ref{subsubsec:sn_classify} are discarded. We are left with a fraction of the original simulated SNe, and that fraction is dependent on a combination of sky location, explosion epoch, redshift, stretch, and colour. The fraction of recovered SNe (the efficiency) is thus described by a 5-dimensional surface. For the $i$th SN the efficiency $\eta_{\mathrm{SN}, i}$ in field $F$, exploding at time $t_0$ at redshift $z$, with stretch $x_1$ and colour $c$, is:
\begin{equation}
    \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i},x_1,c) = \left( \frac{N_{\mathrm{obs}}\left(F_i,z_i,t_{0,i},x_1,c\right)}{N_{\mathrm{sim}}\left(F_i,z_i,t_{0,i},x_{1,i},c_i\right)}\right)\,.
\end{equation}

>>>>

To correct for these incompleteness, we follow a similar method to that used in the Palomar Transient Factory rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}, outlined in \citet{Frohmaier2017}. We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}. We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA}; \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}. We simulate $1.1\times 10^6$ SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$. The SNe are generated and trained in the same way as for the training of SNN. SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}. The SNe are simulated with explosion epochs $t_0$ uniformly distributed between two months before DES-SN began and two months after it finished in order to account for all SNe that could have been observed by DES-SN. We run mock versions of the DES-SN survey, using the exact cadence, conditions, and zeropoints from the survey itself. All of the detected simulated SNe are passed through the light curve fit of SALT2 \citep{Betoule2014}, as per the implementation in \texttt{SNANA}, and those that fail the light curve cuts outlined in Section \ref{subsubsec:sn_classify} are discarded. We are left with a fraction of the original simulated SNe, and that fraction is dependent on a combination of sky location, explosion epoch, redshift, stretch, and colour. The fraction of recovered SNe (the efficiency) is thus described by a 5-dimensional surface. For the $i$th SN the efficiency $\eta_{\mathrm{SN}, i}$ in field $F$, exploding at time $t_0$ at redshift $z$, with stretch $x_1$ and colour $c$, is:
\begin{equation}
    \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i},x_1,c) = \left( \frac{N_{\mathrm{obs}}\left(F_i,z_i,t_{0,i},x_1,c\right)}{N_{\mathrm{sim}}\left(F_i,z_i,t_{0,i},x_{1,i},c_i\right)}\right)\,.
\end{equation}
